Title

### 2019-05-08 4_method.tex
thought out transitions and end-of-markings

\paragraph{point-point segments}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + (\frac12 d)^2}$.
The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{2x}{ \sqrt{4x^2 + d^2}}$
So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
%Wolfram Alpha:
so $\abs x < \frac{d}{2\sqrt{3}} \approx 0.289 d$.
So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.
\hl{But that is very weird in combination with the rule that the ends of marked segments should always be rounded! Isn't it?!}

@@

In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
See \cref{single_bead_strategy_overview}.
We use a distance of the median bead width for the transition.
The transition needs to be robust against extra fingers in the MAT
How do we compute the vertex location of an inset on a finger which crosses a transitional segment in the middle?

By aligning the MAT distance with Euclidean space around the transition locations, we obtain a stable method for determining the vertex locations of insets.
See \cref{distance_rounding_transition}.
The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).

@@

\subsubsection{Ends of markings}
For vertices at the end of a sequence of marked MAT segments we need to perform rounding on the MAT distance measure, so as to avoid a gap being generated by toolapths around that vertex.
See bottom of \cref{rounded_vs_unrounded}.

It impossible for three marked edges to come together.
(Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.

However, \hl{what if we connect two marked segments using a small segment?}
It seems there is some distance limit based on \cref{distance_ratio_limit}.

@@

\subsection{6. transform MAT distance field}
Before generating the locations we can specify a way to space the integer values non-uniformly along a segment.
We can choose have bead widths closer to the nominal bead width near lower MAT dists and do the uniform layout only in the upper region of the segment.
\hl{How do we do this exactly?}

\hl{Is it possible to make this stable against small perturbations?}
See \cref{heterogeneous_joint_generation}.
We must first define a stable end point for where to place the upper region!

@@

How to deal with single beads connecting two polys?
: Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly

How to deal with three-way intersection single beads?
: Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly

>>>>

\paragraph{point-point segments}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + (\frac12 d)^2}$.
The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{2x}{ \sqrt{4x^2 + d^2}}$
So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
%Wolfram Alpha:
so $\abs x < \frac{d}{2\sqrt{3}} \approx 0.289 d$.
So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.

@@

In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
See \cref{single_bead_strategy_overview}.
The transition is such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
The length of the transition along the medial axis depends on the angles involved.
See \cref{transition_length}.
\begin{equation}
t = d_0 (\sin \alpha + \cos \alpha)
\end{equation}

\begin{figure}[H]
\centering
\includegraphics[width=.75\columnwidth]{sources/method/transition_length_v2.pdf}
\caption{Transition length on a line-line segment.}
\label{transition_length}
\end{figure}

\hl{We need a formulation of the MAT distance stranform which defines the MAT distance for any position even if it's not possible to define where the middle of the transition would end up.}

The transition needs to be robust against extra fingers in the MAT.
How do we compute the vertex location of an inset on a finger which crosses a transitioning area?
By interpolating the MAT distance between the two ends of the transition, we obtain a stable method for determining the vertex locations of insets.
See \cref{distance_rounding_transition}.
The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
\hl{Does this hold for any angled wedge? How about point-line segments or point-point segments?}

@@

\subsubsection{Ends of markings}
There are multiple ways in which a sequence of bones starting from the outline polygon can be said to end.
\begin{enumerate}
\item The last node in the sequence is a root node
\item The last node in the sequence is not connected to a marked segment
\end{enumerate}

The MAT distance measure of a root node of the medial axis should always be rounded;
i.e. where the MAT distance measure is a local maximum it should be rounded.
See bottom of \cref{rounded_vs_unrounded}.

For vertices at the end of a sequence of marked MAT segments we need to take care of transitions.
If a transition is overlapping the end of the sequence, then either end of the transition would fall beyond the area where transitions should occur.
How should we deal with thse?
\begin{itemize}
\item We need to keep the transition tick on the marked side, because we need to switch to a different number of ticks somewhere.
Moreover, leaving out the whole transition around end-of-markings would violate the stability principle.
\item The end-of-marking itself will retain its interpolated MAT distance as described above.
\item The transition tick on the non-marked side of discarded.
This means that there will also be no single bead segment leading up to the transition, which coincides with how we deal with non-marked areas.
See \cref{single_bead_strategy}.
\end{itemize}
This method of dealing with end-of-markings can result in gaps slightly larger than usual.
See \cref{change_to_marked}.

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/change_to_marked.pdf}
\caption{before end of markings}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/change_to_marked_2.pdf}
\caption{after end of markings}
\end{subfigure}
\caption{Transition near end of markings. The gap depends on the positioning of the middle of the transition (dotted lines) with respect to the end of the marked areas.}
\label{change_to_marked}
\end{figure}

It impossible for three marked edges to come together.
(Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
However, what if we connect two marked segments using a small non-marked segment?
There is a distance limit based on \cref{distance_ratio_limit}:
the connecting segment is always larger in Euclidean distance than the difference in MAT distance.

@@

\subsection{6. transform MAT distance field}
Before generating the locations we can specify a way to space the integer values non-uniformly along a segment.
We can choose to have bead widths closer to the nominal bead width near lower MAT dists and do the uniform layout only in the upper region of the segment.

This needs to be stable against small perturbations in the outline polygon.
See \cref{heterogeneous_joint_generation}.
For any sequence on non-marked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked medial axis segment.
Based on the MAT distance there we place ticks along the non-marked bones.

@@

We only introduce single bead segments along marked areas of the medial axis.
We could also do it for non-marked areas, but that would result in a small single bead segment at \emph{every} corner.

\hl{How to deal with single beads connecting two polys?}
: Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly

\hl{How to deal with three-way intersection single beads?}
: Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly
